% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[
]{article}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\textbf{Aaron Lorenzo Woods} alwoods@utexas.edu~\textbar{} aaronwoods.info

Department of Biomedical Engineering

Cockrell School of Engineering

The University of Texas at Austin

Austin, TX 78712

\textbf{EDUCATION}

\textbf{Ph.D. Biomedical Engineering} June 2026 \emph{(expected)}

University of Texas at Austin GPA: 4.0

Portfolio in Imaging Science

\textbf{B.S. Engineering Leadership} December 2020

University of Texas at El Paso (UTEP) GPA: 3.46

Minor in Commercial Music and Recording

\textbf{PUBLICATIONS AND PATENTS}

Niemeier, R., Schnoor, N., \textbf{Woods, A.L.,} Rogers, J.D. ``Calibration of liquid crystal variable retarders using a common-path interferometer and fit of a closed-form expression for the retardance curve,'' published to \textbf{Applied Optics}, October 2020.\\
\strut \\
Malady, B., \textbf{Woods, A.L.,} Pogue, M., Purani, H. ``Theranostic Delivery System,'' \textbf{Provisional Patent} Application, No. 63/442436, granted March 2, 2023.

Engelmann, S.A., Tomar, A., \textbf{Woods, A.L.,} Dunn, A.K. ``Pulse train gating to improve signal generation for in vivo two-photon fluorescence microscopy,'' published to \textbf{Neurophotonics,} October 2023.

Chu, D.Y., Ravelli, M.N., Faltersack, K.M., \textbf{Woods, A.L.,} Almane, D., Li, Z., Sampene, E., Felton, E.A. (2023). ``Hypocarnitinemia and its effect on seizure control in adult patients with intractable epilepsy on the modified Atkins diet,'' submitted to \textbf{Frontiers in Nutrition, Nutrition and Metabolism}, September 29, 2023. Manuscript ID: 1304209.

\textbf{RESEARCH EXPERIENCE}

\textbf{Graduate Student Researcher,} University of Texas at Austin 2021 -- Present

Department of Biomedical Engineering \textbar{} \emph{Advisor: Dr. Andrew Dunn}

\begin{itemize}
\item
  Developed optical imaging techniques and alignment of laser microscope systems
\item
  Investigating digital image processing, quantification, and visualization
\item
  Training on surgical craniotomies and animal care for neurovascular imaging
\item
  Conducted experiments, simulations, data analysis, and summarization of findings
\end{itemize}

\textbf{Graduate Rotation Student,} University of Texas at Austin Summer 2021

Department of Biomedical Engineering \textbar{} \emph{Advisor: Dr. Mia Markey}

\begin{itemize}
\item
  Design of decision support system for breast cancer patients
\item
  Collaborated with researchers and clinicians to improve patient care
\item
  Investigated the role of emotions, biases, and heuristics in decision making
\end{itemize}

\textbf{Graduate Rotation Student,} University of Texas at Austin Fall 2021

Department of Biomedical Engineering \textbar{} \emph{Advisor: Dr. Evan Wang}

\begin{itemize}
\item
  Conducted EEG data acquisition and analysis to analyze the brain while sleeping
\item
  Created SOP for fabricating state of the art dry electrodes for long recordings
\item
  Assisted with the design and testing of novel electrode materials
\end{itemize}

\textbf{\hfill\break
}

\textbf{Undergraduate Student Researcher,} University of Texas at El Paso 2019 -- 2020

Create Lab \textbar{} \emph{Advisor: Dr. Peter Golding}

\begin{itemize}
\item
  Innovated on engineering education regarding ethics and leadership
\item
  Programmed advising software to assist with course recommendation
\item
  Optimized the advising process to better facilitate faculty and student
\end{itemize}

\textbf{Undergraduate Student Researcher,} University of Wisconsin-Madison Summer 2019

Adult Neurology Ketogenic Diet Therapy Clinic \textbar{} \emph{Advisor: Dr. Elizabeth Felton}

\begin{itemize}
\item
  Data visualization of patient data for clinical and dietary analysis
\item
  Managed HIPAA compliance, safety, and ethics for patient research
\item
  Shadowed doctor-patient relationship and treatment of epilepsy
\end{itemize}

\textbf{Undergraduate Student Researcher,} University of Wisconsin-Madison Summer 2018

Biomedical Optics Lab \textbar{} \emph{Advisor: Dr. Jeremy Rogers}

\begin{itemize}
\item
  Constructed an interferometer to measure phase delay
\item
  Programmed an automated calibration software for optical equipment
\item
  Inspected laboratory standards and practices for maintaining lab
\end{itemize}

\textbf{RESEARCH FUNDING}

\textbf{Ruth Kirchstein Imaging Science Fellowship,} National Institutes of Health 2021 -- 2022

\begin{itemize}
\item
  \$27,591 awarded over 1 year
\end{itemize}

\textbf{West Texas Fellowship,} The University of Texas at Austin 2022 -- 2024

\begin{itemize}
\item
  \$32,000 awarded over 1 year
\end{itemize}

\textbf{Cockrell School Fellowship}, The University of Texas at Austin 2024 -- 2025

\begin{itemize}
\item
  \$20,000 awarded over one year
\end{itemize}

\textbf{Thrust Fellowship Supplement,} The University of Texas at Austin 2021 -- 2025

\begin{itemize}
\item
  \$36,000 awarded over four years
\end{itemize}

\textbf{Dean's Fellowship Supplement,} The University of Texas at Austin 2021

\begin{itemize}
\item
  \$1,000 awarded over one year
\end{itemize}

\textbf{ACADEMIC APPOINTMENTS}

\textbf{Graduate Student Researcher} Summer 2021 -- Present

University of Texas at Austin, Department of Biomedical Engineering

\textbf{Undergraduate Student Researcher} Fall 2019 -- Spring 2020

UTEP, Department of Engineering Education and Leadership

\textbf{Undergraduate Student Researcher} Summer 2018, 2019

University of Wisconsin-Madison\textbf{,} Department of Biomedical Engineering

\textbf{Undergraduate Teaching Assistant} Spring 2018

UTEP, Department of Engineering Education and Leadership

\textbf{TEACHING EXPERIENCE}

\textbf{Undergraduate Teaching Assistant,} University of Texas at El Paso Spring 2018

Department of Engineering Education and Leadership \textbar{} \emph{Design Nature}

\begin{itemize}
\item
  Coordinated the trainings of students to use a fabrication laboratory
\item
  Taught procedures on computer-aided design and simulation
\item
  Directed the development process to build working prototypes
\end{itemize}

\textbf{HONORS \& AWARDS}

\textbf{Texas Health Catalyst Finalist,} Dell Medical Center 2023

Awarded Industry Mentorship to Commercialize a Product.

\textbf{Marvin \& Ellie Selig Entrepreneurship Award,} Texas Innovation Center 2022

Awarded \$2,500 to advance an entrepreneur effort by developing prototypes.

\textbf{Imaging Science Best Poster Award,} The University of Texas at Austin 2022

\textbf{Engineering Leadership Character Award,} University of Texas at El Paso 2020

Awarded by department to one graduating student with exceptional character.

\textbf{Hunt Startup Sponsorship,} Arrowhead Center 2020

\textbf{Bob \& Diane Malone Leadership Scholarship} University of Texas at El Paso 2016 -- 2020

\textbf{Theta Delta Lambda Education Scholarship,} University of Texas at El Paso 2016

\textbf{Robert G Neill, Jr Scholarship,} University of Texas at El Paso 2016

\textbf{College of Engineering Dean's List,} University of Texas at El Paso 2016 -- 2018

\textbf{POSTER PRESENTATIONS}

\begin{itemize}
\item
  Aaron L. Woods; Andrew K. Dunn. \textbf{Investigating Neurovascular Angiogenesis through Optical Imaging.} University of Texas at Austin T32 Retreat, Austin, TX, USA, May 10, 2022
\item
  Arron L. Woods; Daniel Y. Chu; Michele N. Ravelli; Kelly Faltersack; Elizabeth Felton. \textbf{Carnitine Deficiencies: Clinical Insights for Ketogenic Diet Therapies.} UW- Madison SURE Poster Session, Madison, WI, USA, July 31, 2019
\item
  Arron L. Woods; Jeremy D. Rogers. \textbf{Automated Calibration of Liquid Crystal Variable Retarder}. UW- Madison SURE Poster Session, Madison, WI, USA, July 31, 2018
\item
  ESW-UTEP. Project Mine-Rcycler: \textbf{Producing filament and 3D printed consumer goods from plastic waste.} Engineers for a Sustainable World 2019 Annual Conference Poster Session, El Paso, TX, USA, April 5, 2019
\end{itemize}

\textbf{ACADEMIC SERVICE}

\textbf{Chairman of the Board of Directors,} ICC Austin 2022 -- Present

501(c)(3) Non-Profit \textbar{} \emph{ED: Ashleigh R. Lassiter}

\begin{itemize}
\item
  Facilitated meetings to align groups with the strategic vision and mission.
\item
  Guided discussions with various stakeholders on property management.
\item
  Directed the board\textquotesingle s initial strategic plan to improve staff retention and housing.
\end{itemize}

\textbf{Black Graduate Student Agency Director,} Graduate Student Assembly 2022 -- Present

The University of Texas at Austin

\begin{itemize}
\item
  Built relationships with underrepresented groups committed to equality
\item
  Plan professional development, advocacy, and social events.
\item
  Promote the interests of the graduate student population
\end{itemize}

\textbf{Community Organizer,} Sunrise Movement El Paso 2020 -- 2021

\begin{itemize}
\item
  Strategized solidarity and trust building with local allies
\item
  Plan and organize with other organizations for joint efforts
\item
  Established weekly virtual meetings for safe discussions
\end{itemize}

\textbf{Social Chair,} Green Team (UTEP) 2020

\textbf{Webmaster,} Engineers for a Sustainable World (UTEP) 2017 -- 2019

\textbf{College Recruiter,} University of Texas at El Paso 2018

\textbf{Volunteer Leader,} Young Life College (UTEP) 2016 -- 2018

\textbf{PROFESSIONAL EXPERIENCE}

\textbf{Sr. Intern (Co-op),} \emph{Thermo Fisher Scientific Inc. (MSD)} 2023 -- December 2023

Pioneered a neural network project, applying CNNs for enhanced image classification pivotal to semiconductor defect analysis. Implemented and refined machine learning algorithms using TensorFlow and Keras, leading to improved diagnostic capabilities. Developed a Python script to automate image data collection, yielding a large-scale image repository that facilitated the advancement of AI model training and accuracy in material analysis.

\textbf{Co-founder,} \emph{Therosafe (Startup)} 2021 -- Present

As co-founder of a startup in the field of theranostics, I play a multifaceted role with a focus on operations. I contributed to the development of the company\textquotesingle s concept, deliverables, and presentations, created visualizations to showcase the product, and applied to various competitions to clearly articulate the need we are solving.

\textbf{Community Outreach Specialist,} \emph{University of Texas at El Paso} 2020

Experienced in developing and implementing marketing programs for outreach/recruitment. Assisted in curriculum and materials development. Evaluated program success and adjusted. Conducted program education and exhibit presentations.

\textbf{Project Manager,} \emph{US Army NETCOM} 2020

Project Manager with experience leading a team of engineers to improve military data collection tools. Produced technical reports, organized processes, and evaluated evaluation methods and database UX design.

\textbf{Project Analyst,} \emph{University of Texas at El Paso} 2018 -- 2019

Extracted and visualized retention rates using historical enrollment data. Assisted with in-person, online, and telephone inquiries for academic department operations. Improved the advising process for 200+ students and mentored student staff for future data management and reporting.

\textbf{College Recruiter,} Department of Engineering Education and Leadership 2018 -2020

Experienced in leading STEM events, increasing student enrollment and retention. Implemented innovative sessions for K-12 students.

\textbf{Sound Engineer,} Beacon Hill Recording Studios, LLC 2018 -- 2019

Experienced in microphone placement and sound recording. Verified signal-flow configurations and used industry-standard DAWs for editing and mixing. Collaborated with musicians and producers to deliver high-quality recordings.

\textbf{Student Ambassador,} Amazon \textbar{} Riddle and Bloom 2018 -- 2019

Improved brand awareness through coordinated events with 300+ student interactions. Developed and executed digital, experiential, and peer-to-peer tactics for student engagement. Collaborated with school organizations for growth opportunities and mutual support.

\textbf{Project Finance Engineer,} Sonora Bank 2017

Experienced financial engineer with a focus on personal financial statement design and formatting. Shadowed bank operations and presented financial operations in group meetings. Improved financial operations for community banks.

\textbf{CONFERENCE PARTICIPATION}

\textbf{Latinx Student Leadership Community Summit,} Google 2020

\textbf{Neuroscience Initiative to Enhance Diversity Program,} UC Davis 2020

\textbf{Social Change Leadership Summit,} UTEP 2019 -- 2020

\textbf{Opportunities in Engineering Conference,} UW-Madison 2018

\end{document}
